Pillar 2 - Topic Modeling

### 2019-03-18 Pillar 2 - Topic Modeling.Rmd
rearrange sections

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```
#DELETE LATERRRRRRRRRRRRRRRRRRRRRRRRRRRRRR
Include d_course
```{r d_course}
load("Output/data_general.RDATA")
d_course <- d_course %>% select(`Course ID`, Cluster) %>% distinct

@@

tf_idf_description %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_description")

tf_idf_overview %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_overview")

tf_idf_manual %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_manual")

rm(prepare_tf_idf_concentration, plot_tf_idf,
   tf_idf_description, tf_idf_overview, tf_idf_manual)
```

# LDA
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdmxxxxx}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

d_description_cast <- my_cast_tdm(d_description)
d_overview_cast <- my_cast_tdm(d_overview)
d_manual_cast <- my_cast_tdm(d_manual)

## Ideal Number of Topics (RUN ON UM COMPUTER)
To decide the number of topics to discover, we run (four) three different tests.

First we set the control for the test.
```{r controls, eval = TRUE}
my_control <- list(

@@

```{r fast control}
my_control_fast <- list(

@@

###With Package built in Function
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

>>>>

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```
#DELETE LATERRRRRRRRRRRRRRRRRRRRRRRRRRRRRR
Include d_course
```{r d_course}
load("Output/data_general.RDATA")

@@

tf_idf$overview %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_overview")

tf_idf$manual %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_manual")

rm(prepare_tf_idf_concentration, plot_tf_idf)
```

# LDA
##Setup
###Cast DTM
The function `my_cast_dtm` casts our dataframes into a DTM.
```{r my_cast_dtm, eval = TRUE}
my_cast_dtm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

d_cast <- d_text %>% map(my_cast_dtm)

rm(my_cast_dtm)
```
###Controls
The control parameters we use are:
```{r controls, eval = TRUE}
my_control <- list(

@@

)
```
The control parameters we use for fast testing are:
```{r fast control}
my_control_fast <- list(

@@

##Ideal Number of Topics Package Test
To decide the number of topics to discover, we run three different tests.
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){
